\begin{rubric}{Professional Activities}
%

\subrubric{Public Engagement}
%\entry*[2021]%
%    \textbf{Mini-MBA} course offered by the McMaster Chapter of the Graduate Management Consulting Association.
%
\entry*[2023]%
    \textbf{The Science, Microbes \& Health Podcast} Episode 19: Questioning the existence of a fetal microbiome, with Dr. Kate Kennedy (\url{https://isappscience.org/episode-19-fetal-microbiome/})
%

\subrubric{Professional Development}
%\entry*[2021]%
%    \textbf{Mini-MBA} course offered by the McMaster Chapter of the Graduate Management Consulting Association.
%
\entry*[2022]%
    \textbf{The Carpentries Instructor Training}
%  
\entry*[2019]%
    \textbf{Exploratory Analysis of Biological Data using R} certificate of completion from Canadian Bioinformatics Workshops.
%  
\entry*[2017]%
    \textbf{Data Carpentry} McMaster University.
%
\entry*[2017]%
    \textbf{Software Carpentry: Shell, Git, R} McMaster University.
%
%\pagebreak

\subrubric{Professional Service}
\entry*[2023, 2024]%
    \textbf{Farncombe Research Day Co-Chair,} Farncombe Family Digestive Health Research Institute, McMaster University.
%
\entry*[2023 -- 2025]%
    \textbf{Trainee Representative,} Research Advisory Council, Department of Biochemistry and Biomedical Sciences, McMaster University.
%
\entry*[2022 -- 2026]%
    \textbf{Trainee and ECR Representative,} International DOHaD Society Council.
%
\entry*[2022 -- present]%
    \textbf{Trainee Representative,} Research Advisory Council, Department of Obstetrics and Gynecology, McMaster University.
%
\entry*[2022 -- 2025]%
    \textbf{Seminar Committee,} Department of Biochemistry and Biomedical Sciences, McMaster University.
%
\entry*[2019 -- present]%
    \textbf{Co-Chair of the Farncombe Institute Trainee Association,} Farncombe Family Digestive Health Research Institute, McMaster University.
%    
\entry*[2022 -- 2023]%
    \textbf{Data Management Officer,} Faculty of Health Sciences Postdoctoral Association, McMaster University.
%
%\entry*[2021]%
%    \textbf{Session moderator} Faculty of Health Sciences Plenary, McMaster University.
%
\entry*[2019 -- 2020]%
    \textbf{Logistics Director,} Biochemistry and Biomedical Sciences Research Symposium, McMaster University.
%
\entry*[2018 -- 2019]%
	\textbf{Department Website Committee,} Biochemistry and Biomedical Sciences, McMaster University. 
%
\entry*[2016 -- 2019]%
	\textbf{Co-Chair of "Research in Progress" seminar series,} Farncombe Family Digestive Health Research Institute, McMaster University. 
%
\entry*[2017 -- 2018]%
	\textbf{Graduate Student Seminar Peer Evaluator,} Biochemistry and Biomedical Sciences, McMaster University.	
%
%\entry*[2017]%
%	\textbf{Session moderator and judge,} Canadian National Perinatal Research Meeting, Montebello, Quebec.	
%
%\entry*[2016 -- 2017]%
%	\textbf{Scholarship Ranking Committee,} School of Graduate Studies, McMaster University. 
%

\subrubric{Journal Reviewer}
\entry*[\textit{ad hoc}]%
	Nature Aging, Cell Reports Medicine, Gut Microbes, Microbial Genomics, American Journal of Reproductive Immunology, the Journal of Developmental Origins of Health and Disease, BMC Microbiology,  NPJ Biofilms,  Inflammatory Bowel Diseases
 %
\end{rubric}
