\begin{rubric}{Teaching}
\entry*[2024]%
	\textbf{Introduction to R Workshop} hosted by the Farncombe Institute Trainee Association, McMaster University.
%
\entry*[2016 -- 2023]%
	\textbf{BIOCHEM 4M03: Cellular and Integrated Metabolism (guest lecture)} Department of Biochemistry and Biomedical Sciences, McMaster University.
%
\entry*[2017 -- 2022]%
	\textbf{BIOM 6130: Early Vertebrate Development (guest lecture)} Department of Biomedical Sciences, University of Guelph. 
%
\entry*[2022]%
	\textbf{MS 713: Integrated Systems in Gastrointestinal Health and Disease (guest lecture)} Medical Sciences Graduate Program, McMaster University. 
%	
\entry*[2022]%
	\textbf{Introductory Programming: R} Software Carpentry Workshop offered by the Atlantic Computational Excellence Network (ACENET). 
%
\entry*[2021]%
	\textbf{BIOMEDDC 2W03: Scientific writing for the biomedical sciences (guest lecture)} Department of Biochemistry and Biomedical Sciences, McMaster University. 
%
\entry*[2016 -- 2019]%
	\textbf{Head Teaching Assistant} BIOCHEM 4M03: Cellular and Integrated Metabolism, Department of Biochemistry and Biomedical Sciences, McMaster University.	
%	
%\entry*[2013 -- 2019]%
%	\textbf{Instructor and Course Developer} Prep101.	
%
%\entry*[2012 -- 2013]%
%	\textbf{Teaching Assistant} BIOL 441: Immunology, BIOL 342: Molecular Biotechnology, BIOL 241: Introduction to Applied Microbiology, Department of Biology, University of Waterloo.		
%

\subrubric{Certifications}
\entry*[2024] \textbf{Instructor}. The Carpentries (carpentries.org).
\entry*[2017] \textbf{Teaching and Learning Foundations}. MacPherson Institute, McMaster University.
\end{rubric}